---
title: "Final Project Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cerulean
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(knitr)
library(dbplyr)
library(leaflet)
library(htmltools)
library(tidyr)
library(stopwords)
library(tidytext)
library(wordcloud)
library(shinymeta)

```

## Welcome! 


# About {.tabset}

## Current Sámi activists and Ally Opportunities 

Learn about Pan-Sámi culture and become an Ally by Listening and Reading!

```{r, echo=FALSE}
library(htmltools)

# Define the paths and URLs for the images
image_path1 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/Podcast.png"
link_url1 <- "https://podcasts.apple.com/us/podcast/r%C3%A1jehis-s%C3%A1pmi/id1608443936"

image_path2 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/Samicouncil.png"
link_url2 <- "https://twitter.com/SaamiCouncil/status/1622608329611649026"

image_path3 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/Sami_center.png"
link_url3 <- "https://www.samiculturalcenter.org/"

# Generate HTML code to display the images side by side with adjusted CSS
image_width <- 120
image_height <- 100

image_html1 <- tags$a(tags$img(src = image_path1, width = image_width, height = image_height), href = link_url1)
image_html2 <- tags$a(tags$img(src = image_path2, width = image_width, height = image_height), href = link_url2)
image_html3 <- tags$a(tags$img(src = image_path3, width = image_width, height = image_height), href = link_url3)

# Adjust the CSS styling to make sure images are properly aligned in one row
html <- tagList(
  div(style = "display: flex; justify-content: space-between;", 
      image_html1,
      image_html2,
      image_html3)
)

html

```

### About this Dashboard

This dashboard looks at the **impact of natural electricity windmill
fields** on the ecological and controversial land use issues that the
indigenous people of Scandinavia (Sámi) with specific focus on Reindeer
in Norway through mix method analyses.Please follow me on this journey. First we will understand this projects main focus Indigenous people of Norway's (Sámi people) land rights and the ecological impacts of Windmill fields in Norway. Second we will see visual representations of the windmill fields locations and the impact they have on reindeer historically 1000 year migration patterns and food accessibility through lichen growth. Lastly we will see the poltical sentiment that surrounds recent Norwegian government decisions and indigenous and their ally's activism on Twitter. 

Here are ways you can manipulate the data

-   Filter tweet hashtags

Enjoy!

-   This example dashboard uses social sentiment data extracted from the
    social media platform of Twitter by the author, and observational
    and historical data gathered from social scientists through their
    written insights in journals and open databases and open the
    government database data.gov.

-   **Full citations:**

1.  Rosqvist, G.C., Inga, N. & Eriksson, P. Impacts of climate warming
    on reindeer herding require new land-use strategies. Ambio 51,
    1247--1262 (2022). <https://doi.org/10.1007/s13280-021-01655-2>

2.  Rasmus Kløcker Larsen, Maria Boström, Muonio Reindeer Herding
    District, Vilhelmina Södra Reindeer Herding District, Voernese
    Reindeer Herding District, Jenny Wik-Karlsson,The impacts of mining
    on Sámi lands: A knowledge synthesis from three reindeer herding
    districts,The Extractive Industries and Society,Volume
    9,2022,101051,ISSN 2214-790X,
    <https://doi.org/10.1016/j.exis.2022.101051>.

3.  Tor A. Benjaminsen, Hugo Reinert, Espen Sjaastad & Mikkel Nils Sara

    (2015) Misreading the Arctic landscape: A political ecology of
           reindeer, carrying capacities, and overstocking in Finnmark,
           Norway, Norsk Geografisk Tidsskrift - Norwegian Journal of
           Geography, 69:4, 219-229, DOI: 10.1080/00291951.2015.1031274

4.  Maynard, N.G.1, Oskal, A., Turi, J.M., Mathiesen, S.D., Eira
    ,I.M.G., Yurchak1, B., Etylin,V., Gebelein, J. (2009) Impacts of a
    Changing Climate and Land Use on Reindeer Pastoralism: Indigenous
    Knowledge & Remote Sensing. ntrs.nasa.gov.
    <https://ntrs.nasa.gov/api/citations/20090019721/downloads/20090019721.pdf>

5.  Mendes, Mateus & Menezes, Diogo & Almeida, Jorge Alexandre &
    Farinha, José. (2020). Wind Farm and Resource Datasets: A
    Comprehensive Survey and Overview. Energies. 13. 10.3390/en13184702.

6.  Laestadius,Ann-Helén.(2023).Stolen.translated by Rachel
    Willson-Broyles. United States:Scribner.

7.  Nystad, Kristin, Anna Rita Spein, Benedicte Ingstad. (2014).
    Community resilience factors among indigenous Sa ́mi adolescents:A
    qualitative study in Northern Norway. Transcultural Psychiatr Vol.
    51(5) 651--672.DOI: 10.1177/1363461514532511.

8.  Hausner, VH, Engen, S, Brattland, C, Fauchald, P. Sámi knowledge and
    ecosystem-based adaptation strategies for managing pastures under
    threat from multiple land uses. J Appl Ecol. 2020; 57: 1656-- 1665.
    <https://doi.org/10.1111/1365-2664.13559>

9.  Markkula, I., M. T. Turunen, and S. Kantola. (2019). Traditional and
    local knowledge in land use planning: insights into the use of the
    Akwé: Kon Guidelines in Eanodat, Finnish Sápmi. Ecology and Society
    24(1):20. <https://doi.org/10.5751/ES-10735-240120>

10. Jordan, Stankikos David. Sámi and the climate crisis: The Colonial
    Anthropocene. (2020).thesis. University of Oregon.
    <https://scholarsbank.uoregon.edu/xmlui/bitstream/handle/1794/25765/Final_Thesis-Jordan_N.pdf?sequence=1>.

11. Bjørklund, Ivar. Sápmi - Becoming a Nation: The Emergence of a Sami
    National Community. Tromsø: Tromsø Univ. Museum, 2003.

12. Broderstad, Else Grete. "Political Autonomy and Integration of
    Authority: The Understanding of Saami Self-Determination 1." In
    Indigenous Rights, pp. 249-273. Routledge, 2017.

13. Gaski, L. (2008). Sámi identity as a discursive formation:
    essentialism and ambivalence. In indigenous peoples:
    self-determination, knowledge, indigeneity. Delft: Eburon, p. 219-

14. 

15. Gellner, Ernest. Nations and Nationalism. United Kingdom: Cornell
    University Press, 1983.

16. Gilbert Helen et al. In the Balance: Indigeneity, Performance,
    Globalization. United Kingdom: Liverpool University Press, 2017.

17. Hasselström, Elisabeth. "Representation Construction of Indigeneity
    by State vs Sámi Governments." Thesis. Mittunicweaitetet Mid Sweden
    university, 2022.

18. Hobsbawm, E. J.. Nations and Nationalism Since 1780: Programme,
    Myth, Reality. Spain: Cambridge University Press, 2012.

# Introduction

## Context

### Who are the Sámi people and is Sápmi a Nation?

The Sámi people, also known as Saami or Sami, are indigenous to the
northern parts of Norway, Sweden, Finland, and Russia's Kola Peninsula.
They have a distinct language, culture, and traditional way of life,
heavily dependent on reindeer herding, fishing, and hunting. Despite
being recognized as an indigenous people by the United Nations, the Sámi
have historically faced discrimination and forced assimilation policies,
which have threatened their cultural survival. In recent years, there
have been efforts to promote and protect Sámi rights and cultural
heritage and to protect their lands from exploitation.

```{r}

img3 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/SamiActivists.jpeg" 

img(width = "50%", height = "auto", src = img3, alt = "")
```

Camilla Andersen DEC 15, 2015
(<https://thegroundtruthproject.org/indigenous-people-of-the-arctic-head-home-after-an-historic-climate-agreement/>)

Nations have been drawn and bordered using fabricated notions of
nationness, redistributed, and renamed by its conquerors, and traded and
bought by the elitist governments. In true colonist fashion, Sápmi and
its Sámi caretakers have been added to the sickening multigenerational
Indigenous stories, not unlike the Natives of Australia and those Native
to American and Canada. Sámi land was maliciously stripped of their
original names and cultural significance and placed under the grouped
countries we now call Scandinavia. (Bjørklund 2003) In the words of
Gellner, "Nationalism is not the awakening of nations to
self-consciousness: it invents nations where they do not exist. Before
the ideas of landownership existed and Scandinavian countries became
sovereign nations, borders were not engrained in their citizens minds.
However, the raise of nationalism compelled lands to be renamed in the
image of the country's meticulously constructed national culture.

With Scandinavian nationalism in mind then, the Sámi national movement
must also be defined according to its political positioning in the
Scandinavian law. In 1977, The Swedish government for the first time,
acknowledged the Sámi as a minority people. Norway followed in 1990, and
then Finland in 1995. At this juncture, it is important to point out
that Russia has never recognized Sámi parliament claiming to represent
the Sámi living in the Kola Peninsula till today nor has Russia amended
its constitution to include the Sámi as a recognized minority with
rights: Sámi are invisible and considered effectively erased in elite
minds of the Soviet Union.

Here is a map of the recognized borders of Sápmi and therefore their
land rights.

```{r}
img4 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/sampi.png"

img(width = "100%", height = "60%", src = img4, alt = "")

```

(<https://decolonialatlas.wordpress.com/2021/02/08/sapmi-the-sami-homelands/>)

These small victories in the previously mentioned Scandinavian countries
did not come without tumultuous political debate and continued Sámi
shaming and oppression. This project hopes to show some of the struggles
and recent downturn of these victories that current Norwegian Sámi are
facing.

## 

### Why Did I choose Windmills? Isn't natural energy a good thing for the Enviroment?

There is a misconception surrounding natural energy especially for
Windmill fields.

For one Wind power provides unstable power supply which means that this
power source needs to be supplemented by other sources of power.
Electricity from wind power plants can be stored in batteries but this
is very expensive and requires large resources which many companies
buiding the fields do not budget for or plan on implementing once the
initial build is complete.

This project will show just a small side of Wind power damage. Though it
may produce relatively small amounts of greenhouse gas emissions, the
local damages caused by encroachments in nature and the environment life
cycle are severe.

On the basis of the desire to preserve natural habitats, landscapes and
reindeer herds, wind power is not environmentally friendly, but rather a
largely environmentally harmful form of power generation. This is also a
blatant encroachment on the Sámi indigenous peoples cultural and rights
and the future for reindeer herding.

"Wind power must also be assessed on the basis of the environmental
impacts concerning the production of wind turbines and their
aftereffects. Wind power requires mines for copper, neodymium,
dysprosium, lead, nickel, aluminum, iron, limestone and more, production
plants for generators, turbine blades and foundations, as well as the
blasting and driving connected to assembly of wind power plants. Wind
power generation is far from"emission-free"! Power cables from wind
turbines to consumers also use a lot of metals." (Motvind Norge and
Naturvernforbundet i Ávjovárri 2020:19)

```{r}
img4 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/Windmill_reindeer.png"

img(width = "100%", height = "60%", src = img4, alt = "")

```

# WindMill Location and Lichen Growth statistics

## Let's Look into the Data

### Number of Windmills Per Site

This interactive map visualizes the coordinates for each windmill
field in the country of Norway excluding sites currently under construction. This map demonstrates the location of these windmill fields as being primary built on recognized indigenous land or Sápmi in Norway. 

This data set is a sample of manually collected data from
<https://resdm.com/home>. All rights are reserved by RESDM.

```{r}
GIS <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/GISwindfarms_Norway.csv")
```

```{r}
# Create a leaflet map of the GIS located Windmills in Norway


library(leaflet)

# Create a leaflet map
leaflet(GIS) %>%
  
  # Add the map tiles
  addTiles() %>%
  
  # Add the markers for each point
  addMarkers(
    ~longitude, ~latitude,
    popup = paste(
      "<b>Type:</b>", GIS$type,
      "<br><b>Capacity:</b>", GIS$capacity,
      "<br><b>Turbines:</b>", GIS$turbines,
      "<br><b>Year Online:</b>", GIS$year.online
    )
  )

```

This data set is a sample of manually collected data from
<https://resdm.com/home>. All rights are reserved by RESDM

## Column {tab.set}

### Enviromental decline seasonal timeline from 2010-2019

Fig 1 - LAND INUNDATED: 110 Km2. Hydropower development caused habitat
loss and barriers for reindeer. To estimate its impact, as a baseline
scenario we simulate the removal of magazines built after 1973 in
Setesdal Ryfylke, Norway [Ref: 1]

```{r}

# Define image paths
img1 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/.Before_pastures.png.icloud"
img2 <- "/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/.After_pastures.png.icloud"

img(width = "100%", height = "60%", src = img1, alt = "")


```

Fig 1 zooms in one of the largest hydropower complex in Europe (Blåsjø
and neighbouring magazines). Moving the slider allows to compare the
area flooded BEFORE 1973 (left) & AFTER (right) construction: 110 Km2
were inundated.

Fig 2 - HABITAT LOST: 222 km2. Moving the slider allows to see that an
estimated 222 km2 (or 31 092 soccer fields) of functional reindeer
habitat were lost due to construction of hydropower magazines. 

 **Taken from social science experts** at:
<https://sites.google.com/view/reindeermapsnorway/scenario-analyses?authuser=0>
```{r}

img(width = "100%", height = "60%", src = img2, alt = "")

```

### Lichen Decline or Growth For Reindeer

This data shows the Lichen growth from
2003 and 2015, which intentionally seemed to support a balance of Reindeer herd population in the 21st century until I dug deeper. This data actually confirms the decline of the reindeer population and loss of
traiditonal grazing lands by combining this data with the above images of flooding and ecological change in the surrounding lichen grazing lands that have become inaccessible to migrating reindeer.

**For more information please read what Tor and collegues has to say about this phenomenon.** 

Tor A. Benjaminsen, Hugo Reinert, Espen Sjaastad & Mikkel Nils Sara
(2015) Misreading the Arctic landscape: A political ecology of reindeer,
carrying capacities, and overstocking in Finnmark, Norway, Norsk
Geografisk Tidsskrift - Norwegian Journal of Geography, 69:4, 219-229,
DOI: 10.1080/00291951.2015.1031274

```{r}

lichen <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalDashboard/lichensheet1.csv")



# Create a plot for BigTrees column
ggplot(lichen, aes(x=Site, y=Lichen, fill=factor(BigTrees))) +
  geom_bar(stat="identity") +
  facet_grid(RangeType~Year) +
  labs(x="Site", y="Lichen Percentage", fill="Big Trees") +
  theme_bw() +
  guides(fill=guide_legend(title="Frequency", position="right"))


# Create a plot for SmallTrees column
ggplot(lichen, aes(x=Site, y=Lichen, fill=factor(SmallTrees))) +
  geom_bar(stat="identity") +
  facet_grid(RangeType~Year) +
  labs(x="Site", y="Lichen Percentage", fill="Small Trees") +
  theme_bw() +
  guides(fill=guide_legend(title="Frequency", position="right"))

```

# Twitter Activism 


```{r}
Fosen <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/Fosen-tweets.csv")
SamiRights <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/SamiRights-tweets.csv")
StandwithSápmi <- read.csv("//Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/StandWithSápmi-tweets.csv")
Sami<- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/Sami-tweets.csv")

Sápmi <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/sápmi-tweets.csv")

WindMills <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/WindFarms-tweets.csv")

IndigenousPeoples <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/IndigenousPeoples-tweets.csv")

Samilandrights <- read.csv("/Users/ellievanhattem/Desktop/Desktop - Ellie’s MacBook Air/Spring 2023/Anthro630/FinalProject/Twitter_Hashtags_ANTH630/saamilandrights-tweets.csv")


Samilandrights1 <-Samilandrights
IndigenousPeoples1 <- IndigenousPeoples
WindMills1 <- WindMills
Sápmi1 <- Sápmi
Sami1 <- Sami
StandwithSápmi1 <- StandwithSápmi
SamiRights1 <- SamiRights
Fosen1 <- Fosen



```

```{r}

# Split "date" into two columns that will separate the time and the date values 
# Tag 1 
Fosen1 <- Fosen1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# Fosen1[c("date1", "time")] <-sapply(strsplit(Fosen1$date, " "),c)


Fosen1$time <- substr(Fosen1$time, 1, 8)
# Remove original datetime column

### Tag 2 

SamiRights1 <- SamiRights1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# SamiRights1[c("date1", "time")] <-sapply(strsplit(SamiRights1$date, " "),c)


SamiRights1$time <- substr(SamiRights1$time, 1, 8)
# Remove original datetime column

# Tag 3 
StandwithSápmi1 <- StandwithSápmi1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# StandwithSápmi1[c("date1", "time")] <-sapply(strsplit(StandwithSápmi1$date, " "),c)


StandwithSápmi1$time <- substr(StandwithSápmi1$time, 1, 8)
# Remove original datetime column


# Tag 4 
Sami1 <- Sami1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# Sami1[c("date1", "time")] <-sapply(strsplit(Sami1$date, " "),c)


Sami1$time <- substr(Sami1$time, 1, 8)
# Remove original datetime column


# Tag 5 
Sápmi1 <- Sápmi1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# Sápmi1[c("date1", "time")] <-sapply(strsplit(Sápmi1$date, " "),c)


Sápmi1$time <- substr(Sápmi1$time, 1, 8)
# Remove original datetime column


# Tag 6 
WindMills1  <- WindMills1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# WindMills1 [c("date1", "time")] <-sapply(strsplit(WindMills1 $date, " "),c)


WindMills1 $time <- substr(WindMills1 $time, 1, 8)
# Remove original datetime column



# Tag 7 
IndigenousPeoples1  <- IndigenousPeoples1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# IndigenousPeoples1 [c("date1", "time")] <-sapply(strsplit(IndigenousPeoples1$date, " "),c)


IndigenousPeoples1$time <- substr(IndigenousPeoples1$time, 1, 8)
# Remove original datetime column


# Tag 8 

Samilandrights1 <- Samilandrights1 %>% 
  tidyr::separate(date, into = c("date1", "time"), sep = 11)
# Samilandrights1 [c("date1", "time")] <-sapply(strsplit(Samilandrights1$date, " "),c)


Samilandrights1$time <- substr(Samilandrights1$time, 1, 8)
# Remove original datetime column

```

```{r}
Fosen1$content <- tolower(Fosen1$content)
Sami1$content <- tolower(Sami1$content)
Samilandrights1$content <- tolower(Samilandrights1$content)
SamiRights1$content <- tolower(SamiRights1$content)
IndigenousPeoples1$content <- tolower(IndigenousPeoples1$content)
WindMills1$content <- tolower(WindMills1$content)
Sápmi1$content <- tolower(Sápmi1$content)
StandwithSápmi1$content <- tolower(StandwithSápmi1$content)

```

```{r}

# Defined the keywords to search for
keywords <- c("statsministeren", "politiet", "protestors", "protesting", "windmillparks", "vindmølleparker", "distriktspolitiet", "solidarity", "vindmøllene", "regjeringen", "government")

# Defined countries to search for in the tweets
country <- c("Finland", "America", "Norway", "Sweden", "Fosen", "Norwegian", "American", "Swedish", "Finish")
```

```{r}
# Create a new topic column based on the matches for the different tags dataset

matches_fosen <- sapply(keywords, grepl, x = Fosen1$content, ignore.case = TRUE)
Fosen1$topic <- ifelse(rowSums(matches_fosen) > 0, colnames(matches_fosen)[max.col(matches_fosen)], "Other")

matches_sami <- sapply(keywords, grepl, x = Sami1$content, ignore.case = TRUE)
Sami1$topic <- ifelse(rowSums(matches_sami) > 0, colnames(matches_sami)[max.col(matches_sami)], "Other")

matches_samilandrights <- sapply(keywords, grepl, x = Samilandrights1$content, ignore.case = TRUE)
Samilandrights1$topic <- ifelse(rowSums(matches_samilandrights) > 0, colnames(matches_samilandrights)[max.col(matches_samilandrights)], "Other")

matches_samirights <- sapply(keywords, grepl, x = SamiRights1$content, ignore.case = TRUE)
SamiRights1$topic <- ifelse(rowSums(matches_samirights) > 0, colnames(matches_samirights)[max.col(matches_samirights)], "Other")

matches_indigenous <- sapply(keywords, grepl, x = IndigenousPeoples1$content, ignore.case = TRUE)
IndigenousPeoples1$topic <- ifelse(rowSums(matches_indigenous) > 0, colnames(matches_indigenous)[max.col(matches_indigenous)], "Other")

matches_windmills <- sapply(keywords, grepl, x = WindMills1$content, ignore.case = TRUE)
WindMills1$topic <- ifelse(rowSums(matches_windmills) > 0, colnames(matches_windmills)[max.col(matches_windmills)], "Other")

matches_sapmi <- sapply(keywords, grepl, x = Sápmi1$content, ignore.case = TRUE)
Sápmi1$topic <- ifelse(rowSums(matches_sapmi) > 0, colnames(matches_sapmi)[max.col(matches_sapmi)], "Other")

matches_standwithsapmi <- sapply(keywords, grepl, x = StandwithSápmi1$content, ignore.case = TRUE)
StandwithSápmi1$topic <- ifelse(rowSums(matches_standwithsapmi) > 0, colnames(matches_standwithsapmi)[max.col(matches_standwithsapmi)], "Other")


```

```{r}

# Use pivot_wider to convert the dataframe to wide format
Fosen1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
Sami1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
Samilandrights1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
SamiRights1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
IndigenousPeoples1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
WindMills1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
Sápmi1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")
StandwithSápmi1_wide <- tidyr::pivot_wider(Fosen1, names_from = "topic", values_from = "username")


```

```{r}
#knitr::opts_chunk$set(echo = TRUE) Using this arugment did not help present the data in nice columns like you can have in the markdown before knitting. 

# Define your custom stop words
my_stopwords_en <- c("the", "and", "or", "but", "a", "an", "to", "of", "in", "is", "this", "that", "it", "with", "for", "https", "http", "t.co")

# Create a new data frame with the custom stop words
my_stopwords_en_df <- data.frame(word = my_stopwords_en, language = "en")

no_stopwords <- stopwords::stopwords(language = "norwegian")


no_stopwords_df <- data.frame(word = no_stopwords, lexicon = "no_stopwords")

my_stopwords_en_df <- my_stopwords_en_df %>% mutate(lexicon = "my_stopwords_en")
no_stopwords_df <- no_stopwords_df %>% mutate(language = "no")


# Combine the custom stop word list with the default stop word list
combined_stopwords <- rbind(my_stopwords_en_df, no_stopwords_df)

```

```{r}


# Convert the matrix to a dataframe
fosen_df <- as.data.frame(matches_fosen)
sami_df <- as.data.frame(matches_sami)
samilandrights_df <-as.data.frame(matches_samilandrights)
samirights_df <- as.data.frame(matches_samirights)
indigenous_df <- as.data.frame(matches_indigenous)
windmills_df<- as.data.frame(matches_windmills)
sapmi_df<- as.data.frame(matches_sapmi)
standwithsapmi_df <- as.data.frame(matches_standwithsapmi)

# Reshape the data into a tidy format
fosen_tidy <- fosen_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_fosen")


sami_tidy <- sami_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_sami")



samilandrights_tidy <- samilandrights_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_samilandrights")


samirights_tidy <- samirights_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "samirights_fosen")


indigenous_tidy <- indigenous_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_indigenous")


windmills_tidy <- windmills_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_windmills")


sapmi_tidy <- sapmi_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_sapmi")


standwithsapmi_tidy <- standwithsapmi_df %>%
  pivot_longer(cols = everything(), names_to = "word", values_to = "count") %>%
  mutate(lexicon = ifelse(word %in% combined_stopwords, "combined_stopwords", "none"), dataset = "matches_standwithsapmi")


```

```{r}

# Remove stop words from the content column
fosen1_tidy <- Fosen1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
sami1_tidy <- Sami1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
samilandrights1_tidy <- Samilandrights1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
samirights1_tidy <- SamiRights1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
indigenouspeoples1_tidy <- IndigenousPeoples1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
windmills1_tidy <- WindMills1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
sápmi1_tidy <- Sápmi1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 

# Remove stop words from the content column
StandwithSápmi1_tidy <- StandwithSápmi1 %>%
  unnest_tokens(word, content) %>%
  anti_join(combined_stopwords) 


```

```{r}


# Read in all datasets and add a column specifying the dataset name
samirights1_tidy <- samirights1_tidy %>% 
  mutate(dataset = "SamiRights")
StandwithSápmi1_tidy <- StandwithSápmi1_tidy %>% 
  mutate(dataset = "StandwithSápmi")
sami1_tidy <- sami1_tidy %>% 
  mutate(dataset = "Sami")
sápmi1_tidy <- sápmi1_tidy %>% 
  mutate(dataset = "Sápmi")
windmills1_tidy <- windmills1_tidy %>% 
  mutate(dataset = "WindMills")
indigenouspeoples1_tidy <- indigenouspeoples1_tidy %>% 
  mutate(dataset = "IndigenousPeoples")
samilandrights1_tidy <- samilandrights1_tidy %>% 
  mutate(dataset = "Samilandrights")
fosen1_tidy <- fosen1_tidy %>% 
  mutate(dataset = "Fosen")

# Combine all datasets into a single dataframe
all_tweets <- bind_rows(samilandrights1_tidy, indigenouspeoples1_tidy, windmills1_tidy, sápmi1_tidy, StandwithSápmi1_tidy, samirights1_tidy, fosen1_tidy, sami1_tidy)

# Set the seed for reproducibility
set.seed(123)

# Create a sample of approximately 100 rows per dataset
sample_tweets <- all_tweets %>%
  group_by(dataset) %>%
  sample_n(min(100, n()))

```


## Social Media Activism efforts surrounding Sámi land issues

This social media analysis utilizes the focused data scraping of relevant twitter hashtags provide a larger contextual and political understanding and hopefully a way for you to connect with a platform you might have used or are currently using and the valuable sentiment analysis and inferences that can be made when people come to gather around a common issue. 

First I have created a word cloud of the most used words of each Hashtag that is filterable!

As you can see there are some Norwegian words and English words presented in this data. I have worked with both languages through translation and combining different filtered stopwords/lexicons together to present the data. An interesting thing that I found was that some accounts user names were mentioned in the wordclouds showing their importance in the issues being discussed. 

In future I would like to extend this twitter analysis to filter for the word
Sámi, Norwegian, American, and Indigenous to determine, I hope a general
nationality and the correlation with the previous emotionally
categorized word cloud. 

Next I wanted to show you which Hastags connect the most with people who are passionate about Sápmi issues and the recent Fosen ruling. To best show this I have created a static Chord Diagram that shows #IndigenousPeoples and #Windmills is the most used Hashtags on Twitter (frequency). 


## Toggle down Wordclounds per Tweeter Hashtag

```{r}
# Use the `knitr::include_app` function to embed the Shiny app from shinyapps.io
knitr::include_app("https://vhbarasa.shinyapps.io/FinalProjectWordcloud/", height = "600px")

```
```{r}

library(circlize)
library(dplyr)

# Calculate the count of unique usernames for each dataset
dataset_counts <- sample_tweets %>% 
  distinct(username, dataset) %>% 
  count(dataset) %>%
  arrange(desc(n))

# Create a matrix of dataset counts
matrix_counts <- matrix(dataset_counts$n, nrow = 1)

# Set the names for each dataset
colnames(matrix_counts) <- dataset_counts$dataset

# Create the chord diagram
chordDiagram(matrix_counts, transparency = 0.5)



```